Tabular Constraint Learning

### 2016-04-15 Paper/ECAI/tabular.tex
fixing notation, formalization

\paragraph{Example}
\sergey{need to use this below:}
  For example, a \template \textit{rank} has \CName \textit{$v_r$ = RANK($v_x$)}, where $v_x$ and $v_r$ are its variables; its \CSignature is: groups assigned to $v_x$ must be numeric, groups assigned to $v_y$ must be integer and the length of vectors in $v_x$ is the same as in $v_y$; its \CFunction is the following constraint: the mapping $\{ v_x \mapsto G_x', v_y \mapsto G_y' \}$ is a solution iff $G_x' \subseteq G_x, G_y' \subseteq G_y$ ($G_x \in \groups, G_y \in \groups$) and each value in $G_y'$ is the rank of the corresponding value in $G_x'$ (possibly with ties).

%The constraint \textit{rank} has
%\begin{itemize}
%\item \CName = \textit{$v_r$ = RANK($v_x$)}, where $v_r$ and $v_x$ are %the variables;
%\item \CSignature = subgroup $g_X$ (associated with X) is numeric, $g_Y$ %is integer and the length of vectors in $g_X$ is the same as in $g_Y$; and
%\item
%\CFunction = \textit{$g_Y$ = RANK($g_X$)} iff $g_X \in G_X, g_Y \in G_Y$ %and each value in $g_X$ has the rank (possibly with ties) specified in $%g_Y$.
%\end{itemize}

@@

Let us introduce \template instantiation syntax. Let $S$ be a mapping from variables to the subgroups of \groups and $T$ be a \template, then $T^S$ is the template, in which all variables in all constrainst in \CSignature and \CFunction are instantiated with the corresponding subgroups from $S$. We refer to $T^S$ as a \textit{constraint} and to the instantiated \CSignature (\CFunction) as $\text{\CSignature}^S$ ($\text{\CFunction}^S$).

@@

\subsection{Subgroup satisfaction search}
$\findassignment(\textit{Constraint,Candidates,Solutions})$ is the function that searches for subsets of vectors in the candidate groups that satisfy the constraint.
Every \template~$C$ needs to have an implementation that finds subgroup assignments, given set of tuples each containing a candidate group for every variable in~$C$.

>>>>

\paragraph{Example}
  For example, the \template \textit{rank} has
\begin{itemize}
\item \CName: \textit{$v_r$ = RANK($v_x$)}, where $v_x$ and $v_r$ are its variables;
\item \CSignature: groups assigned to $v_x$ must be numeric, groups assigned to $v_y$ must be integer and the length of vectors in $v_x$ is the same as in $v_y$;
\item \CFunction: the mapping $\{ v_x \mapsto g_x, v_y \mapsto g_y \}$ is a solution iff $g_x \in G_x, g_y \in G_y$ ($G_x \in \groups, G_y \in \groups$) and each value in $g_y$ is the rank of the corresponding value in $g_x$ (possibly with ties).
\end{itemize}

@@

Let us introduce \template instantiation syntax. Let $S$ be a mapping from variables to the subgroups of \groups and $T$ be a \template, then $T^S$ is the template, in which all variables in all constrainst in \CSignature and \CFunction are instantiated with the corresponding subgroups from $S$. We refer to $T^S$ as a \textit{constraint} and to the instantiated \CSignature (\CFunction) as $\text{\CSignature}^S$ ($\text{\CFunction}^S$). Throughout the work we refer as \textit{find constraints} to finding all constraints that hold.

@@

\subsection{Subgroup satisfaction search}
$\findassignment(\textit{Constraint,Candidates,Solutions})$ is the function that searches for subsets of vectors in the candidate groups that satisfy the constraint.
Every \template~$t$ needs to have an implementation that finds subgroup assignments, given set of tuples each containing a candidate group for every variable in~$t$.
